Gaussian Processes Autoregressive Models for the Disturbance Storm Time Index

### 2016-04-25 swsc.tex
Updates from ShareLaTeX

   %\subtitle{I. Overviewing the $\kappa$-mechanism}

@@

Figures \ref{fig:rmse}, \ref{fig:cc}, \ref{fig:deltaDst} and \ref{fig:timingErr} compare the performance of \emph{GP-AR}, \emph{GP-ARX} and the \emph{Persistence} model with the existing results of \citet{Ji2012}. Two central themes come out of these charts.

>>>>

   \subtitle{Extracting predictive performance over and above persistence behavior}

@@

Figures \ref{fig:rmse}, \ref{fig:cc}, \ref{fig:deltaDst} and \ref{fig:timingErr} compare the performance of \emph{GP-AR}, \emph{GP-ARX} and the \emph{Persistence} model with the existing results of \citet{Ji2012}. Figure \ref{fig:rmse} compares the average RMSE of the models over the list of 63 storms, we can see that the \emph{GP-ARX} model gives an improvement of approximately $38\%$ in RMSE with respect to the \emph{TL} model and $60\%$ improvement with respect to the \emph{NM} model.

Two central themes come out of these charts.
